Lab 11 - Missing Data and Imputation:Answers

### 2023-02-15 Lab 11 Missing data/Lab11_MissingData.Rmd
Add files via upload

Compare how models from mice, Amelia, and the above methods perform to our true data:
```{r, eval = FALSE}
#true model
summary(model_true)

#listwise
summary(model_listwise)

#recoding
summary(model_recode)

#mice
summary(pool(model_mice))

#Amelia
summary(pool(models_amelia))
```

>>>>

Compare how models from mice, Amelia, and the above methods perform to our true data:
```{r, eval = FALSE}
# Estimate models
mod <- list()
mod[['True']] <- model_true
mod[['Listwise deletion']] <- model_listwise
mod[['Recoding']] <- model_recode
mod[['Mice']] <- pool(model_mice)
mod[['Amelia']] <- pool(models_amelia)

texreg(mod)

### 2023-02-15 Lab 11 Missing data/Lab11_MissingData_AnswerKey.Rmd
Add files via upload

#Using texreg package to display
texreg(pool(model_mice))

```
So mice is great. Let's also learn about Amelia II (my personal favorite, named after Amelia Earhart, because she is missing). Amelia is a little different because it assumes that your data is jointly distributed as multivariate normal. It uses the "expectation-maximization with bootstrapping" as an algorithm for imputation. The EM algorithm alternates between something called the expectation (E-step) and maximization (M-step) steps until it converges on values that were missing - it converges when the current and previous values are quite close (sounds a bit like Newton Raphson, no?). It brings in bootstraping by doing this process on multiple bootstrapped samples drawn from your original (and incomplete) data.

@@

Compare how models from mice, Amelia, and the above methods perform to our true data:
```{r}
#true model
summary(model_true)

#listwise
summary(model_listwise)

#recoding
summary(model_recode)

#mice
summary(pool(model_mice))

#Amelia
summary(pool(models_amelia))

>>>>

#Using texreg package to display
texreg(pool(model_mice))
```
So mice is great. Let's also learn about Amelia II (my personal favorite, named after Amelia Earhart, because she is missing). Amelia is a little different because it assumes that your data is jointly distributed as multivariate normal. It uses the "expectation-maximization with bootstrapping" as an algorithm for imputation. The EM algorithm alternates between something called the expectation (E-step) and maximization (M-step) steps until it converges on values that were missing - it converges when the current and previous values are quite close (sounds a bit like Newton Raphson, no?). It brings in bootstraping by doing this process on multiple bootstrapped samples drawn from your original (and incomplete) data.

@@

Compare how models from mice, Amelia, and the above methods perform to our true data:
```{r}

# Estimate models
mod <- list()
mod[['True']] <- model_true
mod[['Listwise deletion']] <- model_listwise
mod[['Recoding']] <- model_recode
mod[['Mice']] <- pool(model_mice)
mod[['Amelia']] <- pool(models_amelia)

texreg(mod)
